Problem Set 5

### 2019-11-26 content/assignment/05-problem-set.Rmd
Add problem set 5 rmd

- $Price_h$: price of house $h$ (in thousands of $)
- $Bedrooms_h:$ number of bedrooms in house $h$
- $Baths_h:$ number of bathrooms in house $h$
- $Pool_h: \begin{cases} =1 & \text{if house } h \text{ has a pool} \\ =0 & \text{if house } h \text{ does not have a pool} \end{cases}$
- $View_h: \begin{cases} =1 & \text{if house } h \text{ has a nice view} \\ =0 & \text{if house } h \text{ does not have a nice view} \end{cases}$

### Part A
Suppose he runs the following regression:
$$\widehat{\text{Price}_h}=119.20+29.76 \, \text{Bedrooms}_h+24.09 \, \text{View}_h+14.06 \, (\text{Bedrooms}_h \times \text{View}_h)$$

@@

### Part C
Suppose he runs the following regression:

@@

### Part E
Suppose he runs the following regression:
$$\widehat{\text{Price}_h}=87.90+53.94 \, \text{Bedrooms}_h+15.29 \, \text{Baths}_h+16.19 \, (\text{Bedrooms}_h \times \text{Baths}_h)$$

@@

Interpret the coefficient on cell plans (i.e. $\hat{\beta_1})$

@@

@@

- `infrate`: infant mortality rate (deaths per 100 in population)
- `lead`: $=1$ if city has lead water pipes, $=0$ if did not have lead pipes
- `pH`: water pH

and several demographic variables for 172 U.S. cities in 1900.

@@

@@

Run this joint hypothesis test, and what can you conclude?

@@

### Part G
Make a scatterplot of your log-linear model with a regression line.

### Part H
Put all of your results together in a regression output table with `huxtable` from your answers in questions B, C, G, and H.

>>>>

| Variable | Description |
| `$Price_h$ | price of house $h$ (in thousands of $) |
| $Bedrooms_h$ | number of bedrooms in house $h$ |
| $Baths_h$ | number of bathrooms in house $h$ |
| $Pool_h$ | $\begin{cases} =1 & \text{if house } h \text{ has a pool} \\ =0 & \text{if house } h \text{ does not have a pool} \end{cases}$ |
| $View_h$ |  $\begin{cases} =1 & \text{if house } h \text{ has a nice view} \\ =0 & \text{if house } h \text{ does not have a nice view} \end{cases}$ |

### Part A
Suppose she runs the following regression:
$$\widehat{\text{Price}_h}=119.20+29.76 \, \text{Bedrooms}_h+24.09 \, \text{View}_h+14.06 \, (\text{Bedrooms}_h \times \text{View}_h)$$

@@

### Part C
Suppose she runs the following regression:

@@

### Part E
Suppose she runs the following regression:
$$\widehat{\text{Price}_h}=87.90+53.94 \, \text{Bedrooms}_h+15.29 \, \text{Baths}_h+16.19 \, (\text{Bedrooms}_h \times \text{Baths}_h)$$

@@

@@

## Question 9

@@

| Variable | Description |
| `infrate` | infant mortality rate (deaths per 100 in population) |
| `lead` | $=1$ if city has lead water pipes, $=0$ if did not have lead pipes |
| `pH` | water pH |

> and several demographic variables for 172 U.S. cities in 1900.

@@

## Question 10

@@

> Run this joint hypothesis test, and what can you conclude?

@@

### Part J
Make a scatterplot of your log-linear model with a regression line.

### Part K
Put all of your results together in a regression output table with `huxtable` from your answers in questions B, C, G, and H.
